---
title: "Project_Course_Lab2B"
author: "Reshma.Poeran"
date: "22-2-2021"
output: html_document
---

```{r results='hide'}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(ggrepel)
```

```{r}
citation(package = "tidyverse")
citation(package = "lubridate")
citation(package = "ggplot2")
citation(package = "ggrepel")
```

#### Exercise 1

1. Find a relevant dataset that you recently found or are busy with at the moment*
2. Write a short Rmd report where you LOAD and VISUALIZE (create at least 3 different graphs) the data in an Rmd report.
3. Go over this tutorial: RStudio Params in Rmd
4. Define one parameter in your analysis
5. Knit two different reports of your parameterized Rmd (with two different values for one paramter defined) and sent them to the teacher

Assignment:  
- I want to make an overview with the covid19 cases and deaths in the netherlands per month/year.  
- I will search for a dataset on the internet, uploade the dataset in Rstudio.  
- Analyse the data, what do I need to make an overview and calculate the results.  
- Eventually visualize the figures with a plot.
```{r}
## Load the dataset from the internet
## Source: https://www.ecdc.europa.eu
data <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM", stringsAsFactors = F)

```

```{r warning=FALSE}
## Have a look at the data, what data is in here.
## What information can be used?
view(data)

## What is the structure of the data?
summary(data)

## How many fields are there and what are the names, is there maybe a field I need to add?
names(data)

##Sum of corona cases in total
sum(data$cases)

## Sum of death by corona
sum(data$deaths)

## Add field mnth_year, I will need that to show the result in a plot.
data$mnth_year <- paste0(data$year,data$month)
names(data)

## Filter the data in country on the Netherlands
## Look at the data, is this the information I am looking for?

nl <-
  data %>%
  dplyr::filter(countriesAndTerritories == "Netherlands") 

view(nl)

## I need to prepare my dataset for the plot. 
## I want to group the cases and deaths by month and year.
## Select the fields that are necessary to show the result.

mnth_nl<-
  data %>%
  dplyr::filter(countriesAndTerritories == "Netherlands") %>%
  dplyr::select(c(month,year,cases,deaths,mnth_year)) %>%  
  dplyr::group_by(month,year,mnth_year) %>%
  summarise(sum_cases = sum(cases),
            sum_deaths = sum(deaths)) %>% arrange(year,month)

mnth_nl

## Arrnage the mnth_year field in the correct order, otherwise mnth_year is not in a chronological order.

mnth_nl <- mnth_nl %>%
  mutate(mnth_year = factor(mnth_year,
                            levels = c(201912,20201,20202,20203,20204,
                                       20205,20206,20207,20208,20209,
                                       202010,202011,202012),
                            ordered = TRUE))

## Dataset is ready to visualise.
## I will make a point diagram, sum of the case per month/year.
## And the size of the points and labels show the death count per month/year.

plot_cov19_nl <-
  mnth_nl %>%
  ggplot(aes(x = mnth_year, y = sum_cases, colour = mnth_year)) + 
  geom_point(aes(size = sum_deaths),alpha = 1.0) + 
  geom_label_repel(aes(label=sum_deaths), size = 2.5, box.padding = .5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "bottom",
        )

plot_cov19_nl

```

